Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Mention Glycerin includes a text renderer

At the lowest levels are a simple 3D mathematics library and a library providing
thin C++ wrappers around the components already in OpenGL.  Above that, another
library provides additional utilities for working with OpenGL, including one for
loading volumetric data as a texture.

>>>>

At the lowest levels are a simple 3D mathematics library and a library providing
thin C++ wrappers around the components already in OpenGL.  Above that, another
library provides additional utilities for working with OpenGL, including one for
loading volumetric data as a texture, and another for rendering text.
